An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-23 neurips-19/poly-embed.tex
Changed tikz code out for generated pdfs

\begin{figure}
\begin{center}
\begin{minipage}{0.3\linewidth}
\begin{tikzpicture}
\draw[dashed, opacity=0.2] (-2,0) -- (2,0) node[anchor=north west, opacity=1]{\scriptsize $u_1$};
\draw[dashed, opacity=0.2] (0,-2) -- (0,2)node[anchor=south west, opacity=1]{\scriptsize $u_2$};

\node at (-1,-1){\textbullet} (-1,-1)node[anchor=north east]{\scriptsize $1$};
\node at (1,-1){\textbullet} (1,-1)node[anchor= north west]{\scriptsize $2$};
\node at (1,1){\textbullet} (1,1)node[anchor= south west]{\scriptsize $3$};
\node at (-1,1){\textbullet} (-1,1)node[anchor=south east]{\scriptsize $4$};
\node at (0,0){\textbullet} node[anchor=south west]{\scriptsize $\bot$};

%boxes around each outcome region
\draw[thick] (1/2, 2) -- (1/2, 1/2) -- (2, 1/2);
\draw[thick] (2,-1/2) -- (1/2, -1/2) -- (1/2, -2);
\draw[thick] (-2, 1/2) -- (-1/2, 1/2) -- (-1/2, 2);
\draw[thick] (-2, -1/2) -- (-1/2, -1/2) -- (-1/2, -2);

%lines for subsets
\draw (-3/2, -1/2) -- (1/2, 3/2);
\draw (3/2, -1/2) -- (-1/2, 3/2);
\draw (-1/2, -3/2) -- (3/2, 1/2);
\draw (-3/2, 1/2) -- (1/2, -3/2);

\draw (3/2, -1/2) -- (3/2, 1/2);
\draw (-3/2, -1/2) -- (-3/2, 1/2);
\draw (-1/2, 3/2) -- (1/2, 3/2);
\draw (-1/2, -3/2) -- (1/2, -3/2);

%outcome cell shading
\path[fill=yellow, opacity = 0.1] (2,1/2) -- (1/2,1/2) -- (1/2,2) -- (2,2) -- cycle;
\path[fill=yellow, opacity = 0.1] (-1/2,2) -- (-1/2,1/2) -- (-2,1/2) -- (-2,2) -- cycle;
\path[fill=yellow, opacity = 0.1] (-2,-1/2) -- (-1/2,-1/2) -- (-1/2,-2) -- (-2,-2) -- cycle;
\path[fill=yellow, opacity = 0.1] (1/2,-2) -- (1/2,-1/2) -- (2,-1/2) -- (2,-2) -- cycle;

\draw[fill=green, opacity = 0.5] (1,0) -- (0,1) -- (-1,0) -- (0,-1) -- cycle;

%mark regions where we map to any report
\node at (-7/4, 0){$\R$};
\path[fill=green, opacity=0.5] (-2, 1/2) -- (-3/2, 1/2) -- (-3/2, -1/2) -- (-2, -1/2) -- cycle;

\node at (7/4, 0){$\R$};
\path[fill=green, opacity=0.5] (2, 1/2) -- (3/2, 1/2) -- (3/2, -1/2) -- (2, -1/2) -- cycle;
\node at (0, -7/4){$\R$};
\path[fill=green, opacity=0.5] (-1/2, -2) -- (-1/2, -3/2) -- (1/2, -3/2) -- (1/2, -2) -- cycle;
\node at (0, 7/4){$\R$};
\path[fill=green, opacity=0.5] (-1/2, 2) -- (-1/2, 3/2) -- (1/2, 3/2) -- (1/2, 2) -- cycle;

%where you have two optimal reports
\node at (-1, -5/16){\tiny$1,\bot$};
\path[fill=green, opacity=0.5] (-3/2, -1/2) -- (-1,0) -- (-1/2, -1/2) -- cycle;

\node at (-5/16, -1){\tiny$1,\bot$};
\path[fill=green, opacity=0.5] (-1/2, -3/2) -- (0,-1) -- (-1/2, -1/2) -- cycle;

\node at (1, -5/16){\tiny$2,\bot$};
\path[fill=green, opacity=0.5] (3/2, -1/2) -- (1,0) -- (1/2, -1/2) -- cycle;

\node at (5/16, -1){\tiny$2,\bot$};
\path[fill=green, opacity=0.5] (1/2, -3/2) -- (0,-1) -- (1/2, -1/2) -- cycle;

\node at (5/16, 1){\tiny$3,\bot$};
\path[fill=green, opacity=0.5] (1/2, 3/2) -- (0,1) -- (1/2, 1/2) -- cycle;

\node at (1, 5/16){\tiny$3,\bot$};
\path[fill=green, opacity=0.5] (3/2, 1/2) -- (1,0) -- (1/2, 1/2) -- cycle;

\node at (-1, 5/16){\tiny$4,\bot$};
\path[fill=green, opacity=0.5] (-3/2, 1/2) -- (-1,0) -- (-1/2, 1/2) -- cycle;

\node at (-5/16, 1){\tiny$4,\bot$};
\path[fill=green, opacity=0.5] (-1/2, 3/2) -- (0,1) -- (-1/2, 1/2) -- cycle;

%three optimal reports
\node at (0, -11/8){\tiny$1,2,\bot$};
\path[fill=green, opacity=0.5] (-1/2, -3/2) -- (0,-1) -- (1/2, -3/2) -- cycle;

\node at (-5.1/4,0){\scalebox{0.5}{$1,4,\bot$}};
\path[fill=green, opacity=0.5] (-3/2, -1/2) -- (-1,0) -- (-3/2, 1/2) -- cycle;

\node at (5.1/4,0){\scalebox{0.5}{$2,3,\bot$}};
\path[fill=green, opacity=0.5] (3/2, -1/2) -- (1,0) -- (3/2, 1/2) -- cycle;

\node at (0, 11/8){\tiny$3,4,\bot$};
\path[fill=green, opacity=0.5] (-1/2, 3/2) -- (0,1) -- (1/2, 3/2) -- cycle;

\end{tikzpicture}
\end{minipage}\hfill
\begin{minipage}{0.3\linewidth}
\begin{tikzpicture}
\draw[dashed, opacity=0.2] (-2,0) -- (2,0) node[anchor=north west, opacity=1]{\scriptsize $u_1$};
\draw[dashed, opacity=0.2] (0,-2) -- (0,2)node[anchor=south west, opacity=1]{\scriptsize $u_2$};

\node at (-1,-1){\textbullet} (-1,-1)node[anchor=north east]{\scriptsize $1$};
\node at (1,-1){\textbullet} (1,-1)node[anchor= north west]{\scriptsize $2$};
\node at (1,1){\textbullet} (1,1)node[anchor= south west]{\scriptsize $3$};
\node at (-1,1){\textbullet} (-1,1)node[anchor=south east]{\scriptsize $4$};
\node at (0,0){\textbullet} node[anchor=south west]{\scriptsize $\bot$};

%U_{1,4,\bot}
\draw[fill=blue, fill opacity=0.2] (-2,-1) -- (-2,1) -- (-1,2) -- (1, 0) -- (-1,-2) -- cycle;
\node at (-1/2,0.2){\footnotesize$U_{\{1,4,\bot\}}$};
\path[fill=blue, opacity=0.3] (-1,1) -- (0,0) -- (-1,-1) --cycle;

%U_{2}
\draw[fill=blue, fill opacity=0.2] (1,0) -- (0,-1) -- (1,-2) -- (2, -1) -- cycle;
\node at (1,-0.6){\footnotesize$U_{\{2\}}$};
\end{tikzpicture}
\end{minipage}\hfill
\begin{minipage}{0.3\linewidth}
\begin{tikzpicture}
\draw[dashed, opacity=0.2] (-2,0) -- (2,0) node[anchor=north west, opacity=1]{\scriptsize $u_1$};
\draw[dashed, opacity=0.2] (0,-2) -- (0,2)node[anchor=south west, opacity=1]{\scriptsize $u_2$};

\node at (-1,-1){\textbullet} (-1,-1)node[anchor=north east]{\scriptsize $1$};
\node at (1,-1){\textbullet} (1,-1)node[anchor= north west]{\scriptsize $2$};
\node at (1,1){\textbullet} (1,1)node[anchor= south west]{\scriptsize $3$};
\node at (-1,1){\textbullet} (-1,1)node[anchor=south east]{\scriptsize $4$};
\node at (0,0){\textbullet} node[anchor=south west]{\scriptsize $\bot$};

\draw[thick, fill=green, opacity = 0.5] (1,0) -- (0,1) -- (-1,0) -- (0,-1) -- cycle;
\draw[thick] (2,0) -- (1,0) -- (0,1) -- (0,2);
\draw[thick] (0,2) -- (0,1) -- (-1,0) -- (-2,0);
\draw[thick] (-2,0) -- (-1,0) -- (0,-1) -- (0,-2);
\draw[thick] (0,-2) -- (0,-1) -- (1,0) -- (2,0);

\path[fill=yellow, opacity = 0.1] (2,0) -- (1,0) -- (0,1) -- (0,2) -- (2,2) -- cycle;
\path[fill=yellow, opacity = 0.1] (0,2) -- (0,1) -- (-1,0) -- (-2,0) -- (-2, 2)-- cycle;
\path[fill=yellow, opacity = 0.1] (-2,0) -- (-1,0) -- (0,-1) -- (0,-2) -- (-2,-2) -- cycle;
\path[fill=yellow, opacity = 0.1] (0,-2) -- (0,-1) -- (1,0) -- (2,0) -- (2,-2) -- cycle;
\end{tikzpicture}
\end{minipage}\hfill
\caption{Left: Possible optimal reports given by our $\psi$ constructed using $\|\cdot\|_\infty$ and $\epsilon = 1/2$.  Middle: Two examples of $U \in \U$ and their thickened regions for $\|\cdot\|_1$ and $\epsilon = 1$. Right: Link values given by our $\psi$ constructed using $\|\cdot\|_1$ and $\epsilon = 1$}
\label{fig:abstain-links}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\begin{minipage}{0.3\linewidth}
\includegraphics[width=\linewidth]{./tikz/abstain-link-linf.pdf}
\end{minipage}\hfill
\begin{minipage}{0.3\linewidth}
\includegraphics[width=\linewidth]{./tikz/abstain-link-U-regions-l1.pdf}
\end{minipage}\hfill
\begin{minipage}{0.3\linewidth}
\includegraphics[width=\linewidth]{./tikz/abstain-link-l1.pdf}
\end{minipage}\hfill
\caption{Left: Possible optimal reports given by our $\psi$ constructed using $\|\cdot\|_\infty$ and $\epsilon = 1/2$.  Middle: Two examples of $U \in \U$ and their thickened regions for $\|\cdot\|_1$ and $\epsilon = 1$. Right: Link values given by our $\psi$ constructed using $\|\cdot\|_1$ and $\epsilon = 1$}
\label{fig:abstain-links}
\end{center}
\end{figure}
